Shift-sensitive Power Transformations for Transforming Data to Normality

### 2023-04-06 manuscript/manuscript.Rmd
Outline experimental section.

>>>>

## Datasets with outliers

### Car data

Top gear dataset, weight

### Housing data

Ames housing data set, year built

### Other data ???

## Integration into end-to-end machine learning

- Assess whether shift-invariant robust transformation improves machine learning results.

  - No transformation.
  - Conventional Yeo-Johnson transformation.
  - Shift sensitive Yeo-Johnson transformation.
  - Shift sensitive, robust Yeo-Johnson transformation.
  - Shift sensitive, robust Yeo-Johnson with central normality test.

  TODO: 
  - Add set_lambda, get_lambda, set_shift, get_shift methods.
  - Add option to set p-value for central normality test. Default NULL (no filtering)
  - implement into familiar
